Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-10-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added draft discussion on wall construction

Impact of Instrumentation on Walls?

Impact of Wall Construction

Comparison of Fire Patterns and Flame Heights

@@

\subsection{The Fire Investigators' Challenge}

@@

steep thermal gardiant

>>>>

\section{Comparison of Fire Patterns and Flame Heights}

\subsection{Impact of Instrumentation on Walls}

Compare flame height results IGWB with Fire Pattern Experiments

\subsection{Impact of Wall Construction}

In these experiments, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.  The results from the instrumented gypsum wallboard experiments in Chapter 4, which respresented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.  The corresponding peak temperatures on the face of the gypsum wall board ranged from the    ~$^\circ$C.  This demonstrates the insulatative capability of the gypsum wallboard. Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.

steep thermal gradiant

Therefore with the limited fire exposure time of approximately 300~seconds, and the small, pre-flashover fires used in this study the

@@

\subsection{Modeling Results}

@@
